ITS_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space

### 2023-10-30 paper.qmd
editing pagination

\pagebreak

@@

**ACKNOWLEDGMENTS**

The ITS_LIVE user community for their helpful  feedback.
Pangeo community.
Copernicus Sentinel data processed by ESA.
Landsat data courtesy of the U.S. Geological Survey.
Funding for ITS_LIVE provided by the NASA MEaSUREs program.

>>>>

@@

**Acknowledgments**

* The ITS_LIVE user community for their helpful  feedback.
* Pangeo community.
* Copernicus Sentinel data processed by ESA.
* Landsat data courtesy of the U.S. Geological Survey.
* Funding for ITS_LIVE provided by the NASA MEaSUREs program.

***
